\cventry
{Dec 2024 -- Present}
{Senior C++ Developer}
{IG Group}
{City of London}
{OTC Pricing}
{
    Switched teams to OTC Pricing after a company wide decision to centralise
    Market Making in Krakow. I am now working with a much more expansive estate
    at the heart of IG's core pricing functionality.
    \newline{}
    \textbf{Achievements:}{
	    \begin{itemize}
		    \item{
                Led the adoption of Podman, Nomad and Consul within the department
                and the switch from bare metal deployments to orchestration and
                containers.
            }
	    \end{itemize}
    }
    \textbf{Technologies:}{
        \scriptsize 
            C++17/20, CMake, Conan, Bash, Python, Podman, Nomad, Consul, Gitlab,
            RSSL, Invision
        \newline{} 
    }
}

\cventry
{Sep 2017 -- Dec 2024}
{Senior C++ Developer}
{IG Group}
{City of London}
{Market Making Technology}
{
    Joined the Market Making team initially as a graduate, using C++ 14/17/20 to
    write Market Making applications and integrate them into IG's on-prem exchange
    over FIX with prices distributed over InVision.
    \newline{}
    \textbf{Achievements:}{
	    \begin{itemize}
		    \item{
                Implemented a novel approach to manipulating underlying and
                instrument level datasets using compile time type lists.
            }
		    \item{
                Implemented FIX based price feeds which take in prices from
                external parties and distribute them over TREP infrastructure
            }
            \item{
                Drove automated documentation generation and CI/CD adoption
                within the team.
            }
	    \end{itemize}
    }
    \textbf{Technologies:}{
        \scriptsize 
            C++14/17/20, CMake, Conan, Bash, Python, Gitlab, Invision, FIX, Doxygen,
            MDBook
        \newline{} 
    }
}

\cventry
{Sep 2015 -- Sep 2016}
{Software Engineering Intern}
{Tomo Motor Parts Ltd}
{Uxbridge}
{12 month placement}{
    Responsible for designing, implementing and maintaining a new system to
    integrate with eBay, Royal Mail and an in-house DMS to manage invoicing and
    shipping of eBay orders. I also undertook a variety of other tasks as needed.
    \newline{}
    \textbf{Achievements:}{
        \begin{itemize}
		    \item{
                Integrated with in house C++ DMS over raw sockets by implementing
                its custom binary protocol to create invoices.
            }
            \item{
                Integration with Ebay and Royal Mail through their public API's
            }
		    \item{
                At the time of implementation, it was calculated that the work i
                did saved the company \pounds22,000/yr
            }
        \end{itemize}
    }
    \textbf{Technologies:}{
        \scriptsize 
                Java, SQL, JDBC, Sockets, JavaMail, C3PO, Jetty9, Doxygen, 
                HTML/CSS/JS, Bootstrap, JQuery
        \newline{} 
    }
}


\cventry
{Jul 2015 -- Oct 2015}
{Software Engineering Intern}
{BeSeen Marketing Ltd}
{Beaconsfield}
{Summer Internship}{
    A summer internship using Java in conjunction with Jetty and Selenium to 
    create a functional web testing platform compatible with BrowserStack.
    \newline{}
    \textbf{Achievements:}{
        \begin{itemize}
		    \item{
                Solely responsible for the design and implementation of this
                project.
            }
	    \end{itemize}
    }
    \textbf{Technologies:}{
        \scriptsize
            Java, JDBC, Selenium, Jetty9, Maven, Doxygen,Log4Jv2, HTML/JS/CSS,
            Bootstrap, JQuery
        \newline{} 
    }
}

\cventry
{Jun 2015 -- Jul 2015}
{DevOps Engineer}
{Brunel University}
{Uxbridge}
{Summer Internship}{
    A 5 week internship where I was involved in migrating a webapp
    from a server in leeds to a local server at Brunel University. \newline{}
    \textbf{Achievements:}{
        \begin{itemize}
		    \item{
                Setup and maintained MySQL and Tomcat Servers on Windows Server
                2012.
            }
		    \item{
                Used Javascript, JQuery and MathML to add questions to Maths E.G.
                webapp.
            }
	    \end{itemize}
    }
    \textbf{Technologies:}{
        \scriptsize
            MYSQL, Tomcat, Windows Server 2012, JavaScript, JQuery, MathML
        \newline{}
    }
}

\cventry
{2004--2015}
{Chef}
{Various Restaurants/Hotels/Gastropubs}
{Windsor area}
{Pastry/Garnish/General}{
    \textbf{Technologies:}{
        \scriptsize 
            Knives \& heat 
        \newline{}
    }
}

